Fake News vs Fox News

### 2024-04-19 paper/Fake_News_vs_Fox_News.qmd
delete one unwanted word
last change

---
title: "Fake News vs Fox News"
subtitle: "The Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Party Voters"
author: 
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News. Special thanks to my dear friends Luca Carnegie and Chaitanya Khamar for their love and support; this paper would not have been done so beautifully without your generous help and ideas. Special thanks for Rohan Alexander for his wonderful help and continual support. "
date: today
date-format: long
abstract: "Media consumption has a notable impact on voting behaviour, with the most influential example in the 2020 US presidential elections. Using logistic regression and data from the Cooperative Election Study (CES 2020), I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters. The analysis shows that viewing political-leaning networks significantly impacts voting preferences among voters from all party backgrounds, with CNN viewers more likely to support Biden and Fox News viewers favouring Trump. The findings highlight the media’s role in shaping electoral outcomes, especially its influence on Independent voters, and the importance of addressing challenges posed by media polarization."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump). The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_{10}$)) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively. Media use networks are being represented by the following predictor variables:  $\text{ABC}_i$, $\text{CBS}_i$, $\text{NBC}_i$, $\text{CNN}_i$, $\text{Fox\_News}_i$, $\text{MSNBC}_i$, $\text{PBS}_i$, $\text{Other}_i$. The rest of the predictor variables are denoted as $\text{TV\_type}_i$ and $\text{Party}_i$, where $i$ indexes the individuals in the dataset.

>>>>

---
title: "Fake News vs Fox News"
subtitle: "The Influence of Media Preferences on Voting Behavior in the 2020 U.S. Presidential Election Among Party Voters"
author: 
  - Hannah Yu
thanks: "Code and data are available at: https://github.com/hannahyu07/Fox-News. Special thanks to my dear friends Luca Carnegie and Chaitanya Khamar for their love and support; this paper would not have been done so beautifully without your generous help and ideas. Special thanks to Rohan Alexander for his wonderful help and continual support. "
date: today
date-format: long
abstract: "Media consumption has a notable impact on voting behaviour, with the most influential example in the 2020 US presidential elections. Using logistic regression and data from the Cooperative Election Study (CES 2020), I analyze the relationship between watching specific media networks and voting for either Trump or Biden among Democrat, Republican, Independent, and Other voters. The analysis shows that viewing political-leaning networks significantly impacts voting preferences among voters from all party backgrounds, with CNN viewers more likely to support Biden and Fox News viewers favouring Trump. The findings highlight the media’s role in shaping electoral outcomes, especially its influence on Independent voters, and the importance of addressing challenges posed by media polarization."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
```{r}
#| include: false
#| warning: false
#| message: false

@@

In this model, $y_i$ represents the binary outcome variable indicating whether an individual voted Biden (as opposed to Trump). The probability of voting for the Biden ($\pi_i$) is modeled using a logistic link function (\text{logit}($\pi_i$)), which is a linear combination of the intercept ($\alpha$) and the coefficients ($\beta_1$, $\beta_2$, $\beta_3$, $\beta_4$, $\beta_5$, $\beta_6$, $\beta_7$, $\beta_8$, $\beta_9$, $\beta_{10}$) corresponding to the predictor variables media use networks, TV news type, and party affiliations, respectively. Media use networks are being represented by the following predictor variables:  $\text{ABC}_i$, $\text{CBS}_i$, $\text{NBC}_i$, $\text{CNN}_i$, $\text{Fox\_News}_i$, $\text{MSNBC}_i$, $\text{PBS}_i$, $\text{Other}_i$. The rest of the predictor variables are denoted as $\text{TV\_type}_i$ and $\text{Party}_i$, where $i$ indexes the individuals in the dataset.
